WordRec Experiment

### 2017-07-12 Data_and_analysis/analysis3_pilot.Rmd
pilot experiment 3

The following analysis is done using pilot data with 25 subjects.

We plan to collect data for 100 subjects

@@

d <- read_delim("data_experiment3.txt", delim = " ") %>%
  filter(type == "Task", problem=="No") %>%
  filter(score > 0.5)
```

>>>>

@@

d <- read_delim("data_exp3_pilot6.txt", delim = " ") %>%
  filter(type == "Task", problem=="No") %>%
  filter(score > 0.5)

#Sample size in the real experiment will be 100
```
